```{r setup}
knitr::opts_chunk$set(echo = TRUE, include=TRUE, eval=FALSE, warning=FALSE, message=FALSE)
options(java.parameters = c("-XX:+UseConcMarkSweepGC", "-Xmx12000m"))
library(RSQLite)
library(dplyr)
library(tidyverse)
library(data.table)
library(emmeans)
library(stringr)
library(gridExtra)
library(MASS)
library(mice)
library(mltools)
library(FactoMineR)
library(plyr)
library(ROSE)
library(corrplot)
library(ppclust)
library(cluster)
library(flashClust)
library(factoextra)
library(FSelector)
library(caTools)
library(e1071)
library(caret)
library(caretEnsemble)
library(Amelia)
library(Hmisc)
library(stargazer)
library(utils)
```

# Building the connection
```{r eval = FALSE}
ncm_data_files <- list.files("./Data/")

for (file in ncm_data_files) {
  file_path <- paste0("./Data/", file)
  file_contents <- fread(file_path)
  
  table_name <- gsub(".csv", "", file)
  
  RSQLite::dbWriteTable(for_connection, table_name, file_contents, overwrite = TRUE)
}

RSQLite::dbListTables(for_connection)
```

# Reading the datasets to the database
```{r}
impression_data <- dbGetQuery(for_connection, "SELECT *
                                                FROM impression_data")

creator_demographics <- dbGetQuery(for_connection, "SELECT *
                                                    FROM creator_demographics")

mlog_demographics <- dbGetQuery(for_connection, "SELECT *
                                                 FROM mlog_demographics")

user_demographics <- dbGetQuery(for_connection, "SELECT *
                                                 FROM user_demographics")

fwrite(impression_data, "impression_data_og.csv")
fwrite(creator_demographics, "creator_demographics_og.csv")
fwrite(mlog_demographics, "mlog_demographics_og.csv")
fwrite(user_demographics, "user_demographics_og.csv")

RSQLite::dbDisconnect(for_connection)
```

# Reading the datasets to the environment
```{r}
impression_data <- read_csv("impression_data_og.csv")
creator_demographics <- read_csv("creator_demographics_og.csv")
mlog_demographics <- read_csv("mlog_demographics_og.csv")
user_demographics <- read_csv("user_demographics_og.csv")

# To read faster
saveRDS(impression_data, "impression_data_og.rds")
saveRDS(creator_demographics, "creator_demographics_og.rds")
saveRDS(mlog_demographics, "mlog_demographics_og.rds")
saveRDS(user_demographics, "user_demographics_og.rds")

impression_data <- readRDS("impression_data_og.rds")
mlog_demographics <- readRDS("mlog_demographics_og.rds")
creator_demographics <- readRDS("creator_demographics_og.rds")
user_demographics <- readRDS("user_demographics_og.rds")
```

# Validating the datasets with data dictionary
```{r}
# Removing excess users from impressions table
a <- impression_data %>% group_by(userId) %>% dplyr::summarise(Total_users1 = n())
b <- a %>% dplyr::summarise(total_users = n())

c <- user_demographics %>% group_by(userId) %>% dplyr::summarise(Total_users2 = n())
d <- c %>% dplyr::summarise(total_users = n())

e <- a %>% left_join(c, by = "userId")
(e %>% dplyr::summarise(total_users = n()))

unknown_user <- e %>% filter(is.na(Total_users2))
unknown_user <- unknown_user %>% dplyr::select(userId)

impression_data <- impression_data %>% filter(!(userId %in% unknown_user$userId))
```

# Checking distributions
```{r}
# User data
ggplot(user_demographics, aes(gender)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Gender in User Demographics Dataset", xlab = "gender", ylab = "Count")
ggplot(user_demographics, aes(province)) + geom_histogram(stat = "count") + theme(axis.text.x = element_text(angle = 90)) +
  labs(title = "Distribution of Province in User Demographics Dataset", xlab = "province", ylab = "Count")
ggplot(user_demographics, aes(age)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Age in User Demographics Dataset", xlab = "age", ylab = "Count")
ggplot(user_demographics, aes(level)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Level in User Demographics Dataset", xlab = "level", ylab = "Count")
ggplot(user_demographics, aes(followCnt)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Follow Count in User Demographics Dataset", xlab = "followCnt", ylab = "Count")
ggplot(user_demographics, aes(registeredMonthCnt)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Registered Month Count in User Demographics Dataset", xlab = "registeredMonthCnt", ylab = "Count")

# Impression data
boxplot(impression_data$mlogViewTime, main = "Distribution of mlogViewTime in Impression Dataset", xlab = "mlogViewTime", ylab = "Count") 
ggplot(impression_data, aes(isClick)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of isClick in Impression Dataset", xlab = "isClick", ylab = "Count")
ggplot(impression_data, aes(isComment)) + geom_histogram(stat = "count") +
  labs(title = "Distribution of isComment in Impression Dataset", xlab = "isComment", ylab = "Count")
ggplot(impression_data, aes(isIntoPersonalHomepage)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of isIntoPersonalHomepage in Impression Dataset", xlab = "isIntoPersonalHomepage", ylab = "Count")
ggplot(impression_data, aes(isShare)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of isShare in Impression Dataset", xlab = "isShare", ylab = "Count")
ggplot(impression_data, aes(isViewComment)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of isViewComment in Impression Dataset", xlab = "isViewComment", ylab = "Count")
ggplot(impression_data, aes(isLike)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of isLike in Impression Dataset", xlab = "isLike", ylab = "Count")

# Creator data
ggplot(creator_demographics, aes(gender)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Gender in Creator Demographics Dataset", xlab = "gender", ylab = "Count")
ggplot(creator_demographics, aes(registeredMonthCnt)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Registered Month Count in Creator Demographics Dataset", xlab = "registeredMonthCnt", ylab = "Count")
ggplot(creator_demographics, aes(creatorType)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Creator Type in Creator Demographics Dataset", xlab = "creatorType", ylab = "Count")
ggplot(creator_demographics, aes(level)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Level in Creator Demographics Dataset", xlab = "level", ylab = "Count")

# Card data
ggplot(mlog_demographics, aes(publishTime)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Publish Time in Card Demographics Dataset", xlab = "publishTime", ylab = "Count")
ggplot(mlog_demographics, aes(type)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Type in Card Demographics Dataset", xlab = "type", ylab = "Count")
```

# Preprocessing
```{r}
# Removing outliers - User demographics
outliers <- which(user_demographics$age >= 40)
user_demographics <- user_demographics[-outliers,]
outliers <- which(user_demographics$followCnt >= 200)
user_demographics <- user_demographics[-outliers,]

# NA - User demographics
user_demographics <- user_demographics %>% mutate_all(na_if, "")
user_demographics <- user_demographics %>% mutate_all(na_if, "unknown")
colSums(is.na(user_demographics))
view(user_demographics %>% filter(is.na(level)))
user_demographics <- user_demographics %>% drop_na(level)

missmap(user_demographics)
mice_mod <- mice(user_demographics[, c("age", "level", "followCnt", "registeredMonthCnt")], method = "rf")
saveRDS(mice_mod, "mice_mod.rds")
mice_mod <- readRDS("mice_mod.rds")
na_complete <- complete(mice_mod)
user_demographics$age <- na_complete$age

# NA - Creator demographics
creator_demographics <- creator_demographics %>% mutate_all(na_if, "")
creator_demographics <- creator_demographics %>% mutate_all(na_if, "unknown")
colSums(is.na(creator_demographics))

# Removing outliers - Impressions
outliers <- which(impression_data$mlogViewTime >= 10000)
impression_data <- impression_data[-outliers,]
outliers <- which(impression_data$mlogViewTime < 0)
impression_data <- impression_data[-outliers,]
```

# Preprocessing
```{r}
# Getting swipe count
json <- impression_data %>% dplyr::select(detailMlogInfoList)
json$swipeCnt <- str_count(json$detailMlogInfoList, "\\}")
impression_data <- cbind(impression_data, json$swipeCnt)
names(impression_data)[names(impression_data) == "json$swipeCnt"] <- "swipeCnt"
impression_data$detailMlogInfoList <- NULL
impression_data$swipeCnt <- replace_na(impression_data$swipeCnt, 0)
impression_data <- impression_data %>% mutate(isSwipe = ifelse(swipeCnt > 0, 1, 0))
impression_data$swipeCnt <- NULL

# Removing redundant variables
impression_data <- impression_data[, -c(2:3)]

ggplot(impression_data, aes(isSwipe)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of isSwipe in Impression Dataset", xlab = "isSwipe", ylab = "Count")

saveRDS(impression_data, "impression_data.rds")
saveRDS(user_demographics, "user_demographics.rds")
saveRDS(mlog_demographics, "mlog_demographics.rds")
saveRDS(creator_demographics, "creator_demographics.rds")
```

# Getting master table
```{r}
impression_data <- readRDS("impression_data.rds")
user_demographics <- readRDS("user_demographics.rds")
creator_demographics <- readRDS("creator_demographics.rds")
mlog_demographics <- readRDS("mlog_demographics.rds")

# Getting user data
master_data <- impression_data %>% inner_join(user_demographics, by = "userId")
names(master_data)[names(master_data) == "level"] <- "userLevel"
names(master_data)[names(master_data) == "gender"] <- "userGender"
names(master_data)[names(master_data) == "registeredMonthCnt"] <- "userRegisteredMonthCnt"

# Getting mlog data
master_data <- master_data %>% left_join(mlog_demographics, by = "mlogId")

# Getting creator data
master_data <- master_data %>% left_join(creator_demographics, by = "creatorId")
names(master_data)[names(master_data) == "level"] <- "creatorLevel"
names(master_data)[names(master_data) == "gender"] <- "creatorGender"
names(master_data)[names(master_data) == "registeredMonthCnt"] <- "creatorRegisteredMonthCnt"

saveRDS(master_data, "master_data.rds")
```

# Cleaning the master table to prepare final dataset for modelling
```{r}
master_data <- readRDS("master_data.rds")

# Filtering
master_data[, c("mlogId", "songId", "artistId", "creatorId", "talkId")] <- NULL
colSums(is.na(master_data))
view(master_data %>% filter(is.na(contentId)))
na_data <- which(is.na(master_data$contentId))
master_data <- master_data[-na_data,]

# Getting modelling data
na_data <- which(is.na(master_data$mlogViewTime))
data_for_modelling <- master_data[-na_data,]

# Separate contentId into rows
data_for_modelling$contentId <- data_for_modelling$contentId %>% str_replace_all(",", "")
data_for_modelling$contentId <- data_for_modelling$contentId %>% as.numeric(.)

# Encoding factors
data_for_modelling$userGender <- revalue(data_for_modelling$userGender, c("male" = "0", "female" = "1"))
data_for_modelling$userGender <- as.numeric(data_for_modelling$userGender)
data_for_modelling$creatorGender <- revalue(data_for_modelling$creatorGender, c("male" = "0", "female" = "1"))
data_for_modelling$creatorGender <- as.numeric(data_for_modelling$creatorGender)

# Removing duplicates
data_for_modelling <- distinct(data_for_modelling)

saveRDS(data_for_modelling, "data_for_modelling.rds")
```

# Recency
```{r}
data_for_modelling <- readRDS("data_for_modelling.rds")
data_for_rfe <- data_for_modelling
data_for_rfe <- data_for_rfe %>% mutate(recency = max(dt) - dt)

ggplot(data_for_rfe, aes(recency)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Recency", xlab = "Recency", ylab = "Count")

data_for_rfe <- data_for_rfe %>% mutate(recency_scaled = (recency - min(recency))/(max(recency) - min(recency)))

data_for_rfe %>% ggplot(aes(recency_scaled))+
                  geom_freqpoly() +
                  theme_classic() +
                  ggtitle("Recency Scaled")

# Scree plot for recency
wss <- 0

set.seed(123)
for(i in 1:10){
  km.out <- kmeans(data_for_rfe$recency_scaled, centers = i, nstart = 25)
  wss[i] <- km.out$withinss
  
  print(i)
}

plot(wss, type = "b", xlab = "Number of Clusters", ylab = "Within groups sum of squares", main = "Recency Scree Plot")

set.seed(123)
kmeans_rec = kmeans(data_for_rfe$recency_scaled, centers = 3, nstart = 25)
data_for_rfe$recency_cluster = kmeans_rec$cluster
```

# Frequency
```{r}
get_users <- data_for_rfe %>% group_by(userId) %>% dplyr::summarise(frequency = n())
data_for_rfe <- data_for_rfe %>% left_join(get_users, by = "userId")

ggplot(data_for_rfe, aes(frequency)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Frequency", xlab = "Frequency", ylab = "Count")

data_for_rfe <- data_for_rfe %>% mutate(frequency_scaled = (frequency - min(frequency))/(max(frequency) - min(frequency)))

data_for_rfe %>% ggplot(aes(frequency_scaled))+
                  geom_freqpoly() +
                  theme_classic() +
                  ggtitle("Frequency Scaled")

# Scree plot for frequency
wss <- 0

set.seed(123)
for(i in 1:10){
  km.out <- kmeans(data_for_rfe$frequency_scaled, centers = i, nstart = 25)
  wss[i] <- km.out$withinss
  
  print(i)
}

plot(wss, type = "b", xlab = "Number of Clusters", ylab = "Within groups sum of squares", main = "Frequency Scree Plot")

set.seed(123)
kmeans_freq = kmeans(data_for_rfe$frequency_scaled, centers = 3, nstart = 25)
data_for_rfe$frequency_cluster = kmeans_freq$cluster
```

# Engagement
```{r}
data_for_rfe <- data_for_rfe %>% mutate(engagement = dplyr::select(data_for_rfe,
                                                             isClick,
                                                             isComment,
                                                             isIntoPersonalHomepage,
                                                             isShare,
                                                             isViewComment,
                                                             isLike,
                                                             isSwipe,
                                                             mlogViewTime) %>%
                                             rowSums(.))

ggplot(data_for_rfe, aes(engagement)) + geom_histogram(bins = 500) + 
  labs(title = "Distribution of Engagement", xlab = "Frequency", ylab = "Count")

data_for_rfe <- data_for_rfe %>% mutate(engagement_scaled = (engagement - min(engagement))/(max(engagement) - min(engagement)))

data_for_rfe %>% ggplot(aes(engagement_scaled))+
                  geom_freqpoly() +
                  theme_classic() +
                  ggtitle("Engagement")
summary(data_for_rfe)

# Scree plot engagement
wss <- 0

set.seed(123)
for(i in 1:10){
  km.out <- kmeans(data_for_rfe$engagement_scaled, centers = i, nstart = 25)
  wss[i] <- km.out$withinss
  
  print(i)
}

plot(wss, type = "b", xlab = "Number of Clusters", ylab = "Within groups sum of squares", main = "Engagement Scree Plot")

set.seed(123)
kmeans_eng = kmeans(data_for_rfe$engagement_scaled, centers = 3, nstart = 25)
data_for_rfe$engagement_cluster = kmeans_eng$cluster

saveRDS(data_for_rfe, "data_for_rfe.rds")
```

# Overall Score
```{r}
data_for_rfe <- data_for_rfe %>% mutate(engagement_score = ifelse(engagement_cluster == 3, 2,
                                                                         ifelse(engagement_cluster == 2, 3, 1)))

data_for_rfe <- data_for_rfe %>% mutate(recency_score = ifelse(recency_cluster == 3, 2,
                                                               ifelse(recency_cluster == 2, 3, 1)))

data_for_rfe <- data_for_rfe %>% mutate(frequency_score = ifelse(frequency_cluster == 3, 3,
                                                                 ifelse(frequency_cluster == 2, 1, 2)))

data_for_rfe <- data_for_rfe %>% mutate(overall_score = dplyr::select(data_for_rfe,
                                                                      engagement_score,
                                                                      recency_score,
                                                                      frequency_score) %>%
                                          rowSums(.))

saveRDS(data_for_rfe, "data_for_rfe.rds")
```

# Active User Classification
```{r}
get_user_score <- data_for_rfe %>% group_by(userId) %>% dplyr::summarise(userScore = sum(overall_score))
data_for_rfe <- data_for_rfe %>% left_join(get_user_score, by = "userId")

data_for_rfe <- data_for_rfe %>% mutate(isActive = ifelse(userScore <= mean(userScore), 0, 1))
data_for_rfe$isActive <- as.factor(data_for_rfe$isActive)

table(data_for_rfe$isActive)

saveRDS(data_for_rfe, "data_for_rfe.rds")
data_for_rfe <- readRDS("data_for_rfe.rds")
```

# Exploratory
```{r}
data_for_rfe <- readRDS("data_for_rfe.rds")

data_for_glm <- data_for_rfe
data_for_glm <- data_for_glm %>% na.omit(.)
data_for_glm$userId <- NULL
data_for_glm$userLevel <- NULL
data_for_glm <- data_for_glm %>% dplyr::select(-c("recency_scaled", "recency_cluster", 
                                                  "frequency_scaled", "frequency_cluster", 
                                                  "engagement_scaled", "engagement_cluster", 
                                                  "userScore"))

# Distribution of numerical data
ggplot(data_for_glm, aes(log(mlogViewTime))) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of mlogViewTime", xlab = "mlogViewTime", ylab = "Count")

ggplot(data_for_glm, aes(age)) + geom_histogram(stat = "count") +
  labs(title = "Distribution of User Age", xlab = "Age", ylab = "Count")

ggplot(data_for_glm, aes(userRegisteredMonthCnt)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Registered Month Count of User", xlab = "userRegisteredMonthCnt", ylab = "Count")
data_for_glm <- data_for_glm %>% filter(userRegisteredMonthCnt <= 100)

ggplot(data_for_glm, aes(log(followCnt))) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Follow Count of User", xlab = "followCnt", ylab = "Count")

ggplot(data_for_glm, aes(publishTime)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Publish Time of the Card", xlab = "publishTime", ylab = "Count")

ggplot(data_for_glm, aes(creatorRegisteredMonthCnt)) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Registered Month Count of Creator", xlab = "creatorRegisteredMonthCnt", ylab = "Count")

ggplot(data_for_glm, aes(log(follows))) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Follow Count of Creator", xlab = "Follows", ylab = "Count")

ggplot(data_for_glm, aes(sqrt(followeds))) + geom_histogram(stat = "count") + 
  labs(title = "Distribution of Followers of Creator", xlab = "Followers", ylab = "Count")

data1 <- data_for_glm[1:50000, ]
data2 <- data_for_glm[50001:100000, ]
data3 <- data_for_glm[100001:150000, ]
data4 <- data_for_glm[150001:200000, ]
data5 <- data_for_glm[200001:250000, ]
data6 <- data_for_glm[250001:300000, ]
data7 <- data_for_glm[300001:350000, ]
data8 <- data_for_glm[350001:400000, ]
data9 <- data_for_glm[400001:450000, ]
data10 <- data_for_glm[450001:500000, ]
data11 <- data_for_glm[500001:553452, ]

glm_model <- glm(isActive ~ ., family = "binomial", data = data1)
glm_model <- update(glm_model, data = data2)
glm_model <- update(glm_model, data = data3)
glm_model <- update(glm_model, data = data4)
glm_model <- update(glm_model, data = data5)
glm_model <- update(glm_model, data = data6)
glm_model <- update(glm_model, data = data7)
glm_model <- update(glm_model, data = data8)
glm_model <- update(glm_model, data = data9)
glm_model <- update(glm_model, data = data10)
glm_model <- update(glm_model, data = data11)

saveRDS(glm_model, "glm_model.rds")
glm_model <- readRDS("glm_model.rds")

summary(glm_model)

stargazer::stargazer(glm_model, type = "text", title = "GLM Summary Statistics", out = "glm_model.txt", single.row = T, align = T, flip = T)

# Correlation matrix
summary(data_for_glm)
data_for_cor <- data_for_glm
data_for_cor$isActive <- data_for_cor$isActive %>% as.numeric(.)
cor_attr <- data_for_cor %>% dplyr::select(-c("province")) %>% cor(.) %>% data.frame(.)
active <- data.frame(cor_attr$isActive)
active$parameter <- row.names(cor_attr)
names(active) <- c("Correlation", "Parameter")
active

# Visualisation of correlation plots, contrıbutıon plots, and PCA
corrplot(cor(data_for_cor %>% dplyr::select(-c("province")), use = "complete.obs"), type = "upper", method = "ellipse", tl.cex=0.9)

PCA(data_for_cor %>% dplyr::select(-c("province", "isActive", "dt", "engagement", "follows", "overall_score", "isShare", "isIntoPersonalHomepage", "contentId", "followeds", "creatorType", "creatorLevel", "engagement_score", "recency_score", "frequency_score")), scale.unit = TRUE, ncp = 5, graph = TRUE)

result_pca <- PCA(data_for_cor %>% dplyr::select(-c("province", "isActive", "dt", "engagement", "follows", "overall_score", "isShare",
                                                    "isIntoPersonalHomepage", "contentId", "followeds", "creatorType", "creatorLevel",
                                                    "engagement_score", "recency_score", "frequency_score")), 
                  scale.unit = TRUE, ncp = 5, graph = FALSE)
print(result_pca)
eigenvalue <- get_eigenvalue(result_pca)
print(eigenvalue)
fviz_eig(result_pca, addlabels = TRUE, ylim = c(0, 15), font.xt = 12)

var_pca <- get_pca_var(result_pca)
corrplot(var_pca$cos2, is.corr = FALSE)
fviz_cos2(result_pca, choice = "var", axes = 1:2, font.xt = 12)

corrplot(var_pca$contrib, is.corr = FALSE)
fviz_contrib(result_pca, choice = "var", axes = 1, top = 10, font.xt = 12)
fviz_contrib(result_pca, choice = "var", axes = 2, top = 10, font.xt = 12)

modelling_data <- data_for_glm %>% dplyr::select(-c("dt", "engagement", "follows", "overall_score", "isShare", "isIntoPersonalHomepage",
                                                    "contentId", "followeds", "creatorType", "creatorLevel", "engagement_score", 
                                                    "recency_score", "frequency_score"))
modelling_data_for_clusters <- data_for_glm %>% dplyr::select(-c("dt", "engagement", "follows", "overall_score", "isShare",
                                                                 "isIntoPersonalHomepage", "contentId", "followeds", "creatorType",
                                                                 "creatorLevel", "engagement_score", "recency_score", "frequency_score"))
```

# Balancing the data
```{r}
# Checking the structure
str(modelling_data)

# Encoding for province variable
modelling_data$province <- as.factor(modelling_data$province)
modelling_data <- one_hot(as.data.table(modelling_data), cols = "province")
for(col in 7:41){
    colnames(modelling_data)[col] <- sub(" ", "_", colnames(modelling_data)[col])
    colnames(modelling_data)[col] <- sub(" ", "", colnames(modelling_data)[col])
}

# Test and training data
set.seed(123)
split = sample.split(modelling_data$isActive, SplitRatio = 0.70)
training_data = subset(modelling_data, split == TRUE)
test_data = subset(modelling_data, split == FALSE)

# Balancing the data with 40% proportion
prop.table(table(training_data$isActive)) * 100
bothsampled <- ovun.sample(isActive ~ ., data = training_data, method = "both", p = 0.4, seed = 1)$data
prop.table(table(bothsampled$isActive)) * 100

saveRDS(modelling_data, "modelling_data.rds")
saveRDS(modelling_data_for_clusters, "modelling_data_for_clusters.rds")
saveRDS(bothsampled, "bothsampled.rds")
```

# Naive Bayes Model
```{r}
bothsampled <- readRDS("bothsampled.rds")

# Modelling
model_naive <- train(isActive~., data = bothsampled, method = "nb", 
                     trControl = trainControl(method = "cv", number = 5))
saveRDS(model_naive, "model_naive.rds")
model_naive <- readRDS("model_naive.rds")
plot(model_naive)

# Evaluating
predict_naive <- predict(model_naive, newdata = test_data)
saveRDS(predict_naive, "predict_naive.rds")
predict_naive <- readRDS("predict_naive.rds")

# Attribute performance
imp_attr_naive <- varImp(model_naive)
plot(imp_attr_naive, main = "Variable Importance of Naive Bayes")

# Confusion
naive_cm <- table(test_data$isActive, predict_naive)
confusionMatrix(naive_cm)

# Looking at the predictions
view(head(cbind(predict_naive, test_data), 20))
```

# K-Nearest Neighbour Model
```{r}
model_knn <- train(isActive~., data = bothsampled, method = "knn", 
                   trControl = trainControl(method = "cv", number = 5))
saveRDS(model_knn, "model_knn.rds")
model_knn <- readRDS("model_knn.rds")
plot(model_knn)

# Evaluating
predict_knn <- predict(model_knn, newdata = test_data)
saveRDS(predict_knn, "predict_knn.rds")
predict_knn <- readRDS("predict_knn.rds")
predict_knn_prob <- predict(model_knn, test_data, "prob")

# Attribute performance
imp_attr_knn <- varImp(model_knn)
plot(imp_attr_knn, main = "Variable Importance of K-NN")

#Confusion matrix
knn_cm <- table(test_data$isActive, predict_knn)
confusionMatrix(knn_cm)

#Looking at the predictions
view(head(cbind(predict_knn, test_data), 20))

library(pROC)
multiclass.roc(test_data$isActive, predict_knn, plot=T, percent = TRUE)
```

# Hybrid Model
```{r}
bothsampled_hydrid <- bothsampled %>% mutate(isActive = ifelse(isActive == 1, "Active", "Inactive"))
test_data_hydrid <- test_data %>% mutate(isActive = ifelse(isActive == 1, "Active", "Inactive"))

model_hybrid <- caretList(isActive ~., data = bothsampled_hydrid, trControl = trainControl(method = "cv", number = 5, classProbs = TRUE),
                          methodList = c("nb", "knn"))
model_hybrid <- readRDS("model_hybrid.rds")

output <- resamples(model_hybrid)
summary(output)
dotplot(output)

stack <- caretStack(model_hybrid, method = "glm", trControl = trainControl(method = "cv", number = 5))

predict_hybrid <- predict(stack, test_data)
predict_hybrid <- readRDS("predict_hybrid.rds")

# Confusion matrix
hybrid_cm <- table(test_data_hydrid$isActive, predict_hybrid)
confusionMatrix(hybrid_cm)
```

# Model Comparison
```{r}
results <- resamples(list(NAIVE = model_naive, KNN = model_knn, HYBRID_NAIVE = model_hybrid[[1]], HYBRID_KNN = model_hybrid[[2]]))

scales <- list(x = list(relation = "free"), y = list(relation = "free"))

bwplot(results, scales = scales)

significances <- diff(results)
summary(significances)
```

# Characteristics and Preferences of Active Users
## Perspective 1
```{r}
data_for_clustering <- modelling_data_for_clusters %>% dplyr::select(c("province", "age", "type", "publishTime", "userRegisteredMonthCnt",
                                                          "creatorRegisteredMonthCnt", "followCnt", "userGender", "isActive"))

data_for_clustering <- data_for_clustering %>% mutate(type = ifelse(type == 1, "Image", "Video"))
data_for_clustering <- data_for_clustering %>% mutate(userGender = ifelse(userGender == 1, "femaleUser", "maleUser"))
data_for_clustering <- data_for_clustering %>% filter(isActive == 1)
data_for_clustering$isActive <- NULL

data_for_clustering <- data_for_clustering %>%
  group_by(province, userGender, type) %>%
  dplyr::summarise(age = mean(age),
            publishTime = mean(publishTime),
            userRegisteredMonthCnt = mean(userRegisteredMonthCnt),
            creatorRegisteredMonthCnt = mean(creatorRegisteredMonthCnt),
            followCnt = mean(followCnt)) %>%
  tidyr::pivot_wider(names_from = province, values_from = c(age, publishTime, userRegisteredMonthCnt, creatorRegisteredMonthCnt, followCnt), 
                     values_fill = 0)

data_for_clustering <- data_for_clustering %>%
  pivot_longer(1:2, names_to = "attribute", values_to = "value")

data_for_clustering <- data_for_clustering %>% group_by(attribute, value) %>% dplyr::summarise(across(everything(), list(mean)))
data_for_clustering$attribute <- paste0(data_for_clustering$attribute, data_for_clustering$value)
data_for_clustering$value <- NULL
data_for_clustering$attribute[which(data_for_clustering$attribute == "typeImage")] <- "Image"
data_for_clustering$attribute[which(data_for_clustering$attribute == "typeVideo")] <- "Video"
data_for_clustering$attribute[which(data_for_clustering$attribute == "userGenderfemaleUser")] <- "femaleUser"
data_for_clustering$attribute[which(data_for_clustering$attribute == "userGendermaleUser")] <- "maleUser"
data_for_clustering$attribute <- as.factor(data_for_clustering$attribute)
data_for_clustering <- data_for_clustering %>% remove_rownames %>% column_to_rownames(var="attribute")

# Scree plot for province
wss <- 0

set.seed(123)
for(i in 1:3){
  km.out <- kmeans(data_for_clustering, centers = i, nstart = 25)
  wss[i] <- km.out$withinss

  print(i)
}

plot(wss, type = "b", xlab = "Number of Clusters", ylab = "Within groups sum of squares", main = "Scree Plot for Type and User Genders Grouped By Province")

set.seed(123)
kmeans_all <- kmeans(data_for_clustering, centers = 2, nstart = 25)
data_for_clustering <- as.data.frame(data_for_clustering)
data_for_clustering$cluster <- kmeans_all$cluster

fviz_cluster(kmeans_all, data = data_for_clustering)
table(data_for_clustering$cluster)

cluster_summary <- aggregate(data_for_clustering, by = list(cluster=kmeans_all$cluster), mean)
cluster_summary <- round(cluster_summary, 0)
cluster_summary <- cluster_summary %>%
  pivot_longer(2:161, names_to = "province", values_to = "value")
cluster_summary_age <- cluster_summary[c(1:32, 161:192),]
cluster_summary_publishTime <- cluster_summary[c(33:64, 193:224),]
cluster_summary_userRegisteredMonthCnt <- cluster_summary[c(65:96, 225:256),]
cluster_summary_creatorRegisteredMonthCnt <- cluster_summary[c(97:128, 257:288),]
cluster_summary_followCnt <- cluster_summary[c(129:160, 289:320),]

age_lm <- lm(value ~ cluster, cluster_summary_age)
age_emm <- emmeans(age_lm, ~ cluster)
age_contrast <- confint(pairs(age_emm, reverse = TRUE))
avg_age <- grid.arrange(ggplot(summary(age_emm), aes(y = emmean, x = cluster, ymin = lower.CL, ymax = upper.CL, color = cluster)) +
                          geom_point() + geom_linerange() + geom_hline(yintercept = 0, lty = 2) +
                          labs(x = "Cluster", y = "Average Age", colour = "Cluster", title = "Average Ages for Each Cluster",
                               subtitle = "Error bars are 95% CIs"),
                        ggplot(age_contrast, aes(y = estimate, x = contrast, ymin = lower.CL, ymax = upper.CL)) +
                          geom_point() + geom_linerange() + geom_hline(yintercept = 0, lty = 2) +
                          labs(x = "Cluster", y = "Average Age", colour = "Cluster", 
                               title = "Difference Between the Average Ages for Each Cluster", subtitle = "Error bars are 95% CIs"))

publishTime_lm <- lm(value ~ cluster, cluster_summary_publishTime)
publishTime_emm <- emmeans(publishTime_lm, ~ cluster)
publishTime_contrast <- confint(pairs(publishTime_emm, reverse = TRUE))
avg_publishTime <- grid.arrange(ggplot(summary(publishTime_emm), 
                                       aes(y = emmean, x = cluster, ymin = lower.CL, ymax = upper.CL, color = cluster)) +
                                  geom_point() + geom_linerange() + geom_hline(yintercept = 0, lty = 2) +
                                  labs(x = "Cluster", y = "Average Publish Time", colour = "Cluster", 
                                       title = "Average Publish Times for Each Cluster", subtitle = "Error bars are 95% CIs"),
                                ggplot(publishTime_contrast, aes(y = estimate, x = contrast, ymin = lower.CL, ymax = upper.CL)) +
                                  geom_point() + geom_linerange() + geom_hline(yintercept = 0, lty = 2) +
                                  labs(x = "Cluster", y = "Average Publish Time", colour = "Cluster", 
                                  title = "Difference Between the Average Publish Times for Each Cluster", subtitle = "Error bars are 95% CIs"))

userRegisteredMonthCnt_lm <- lm(value ~ cluster, cluster_summary_userRegisteredMonthCnt)
userRegisteredMonthCnt_emm <- emmeans(userRegisteredMonthCnt_lm, ~ cluster)
userRegisteredMonthCnt_contrast <- confint(pairs(userRegisteredMonthCnt_emm, reverse = TRUE))
avg_userRegisteredMonthCnt <- grid.arrange(ggplot(summary(userRegisteredMonthCnt_emm), 
                                                  aes(y = emmean, x = cluster, ymin = lower.CL, ymax = upper.CL, color = cluster)) +
                                             geom_point() + geom_linerange() + geom_hline(yintercept = 0, lty = 2) +
                                             labs(x = "Cluster", y = "Average User Registered Month Count", colour = "Cluster", 
                                             title = "Average User Registered Month Count for Each Cluster", subtitle = "Error bars are 95% CIs"),
                                           ggplot(userRegisteredMonthCnt_contrast, 
                                                  aes(y = estimate, x = contrast, ymin = lower.CL, ymax = upper.CL)) +
                                             geom_point() + geom_linerange() + geom_hline(yintercept = 0, lty = 2) +
                                             labs(x = "Cluster", y = "Average User Registered Month Count", colour = "Cluster", 
                                             title = "Difference Between the Average User Registered Month Counts for Each Cluster", 
                                             subtitle = "Error bars are 95% CIs"))

creatorRegisteredMonthCnt_lm <- lm(value ~ cluster, cluster_summary_creatorRegisteredMonthCnt)
creatorRegisteredMonthCnt_emm <- emmeans(creatorRegisteredMonthCnt_lm, ~ cluster)
creatorRegisteredMonthCnt_contrast <- confint(pairs(creatorRegisteredMonthCnt_emm, reverse = TRUE))
avg_creatorRegisteredMonthCnt <- grid.arrange(ggplot(summary(creatorRegisteredMonthCnt_emm), 
                                                  aes(y = emmean, x = cluster, ymin = lower.CL, ymax = upper.CL, color = cluster)) +
                                             geom_point() + geom_linerange() + geom_hline(yintercept = 0, lty = 2) +
                                             labs(x = "Cluster", y = "Average Creator Registered Month Count", colour = "Cluster", 
                                             title = "Average Creator Registered Month Count for Each Cluster", 
                                             subtitle = "Error bars are 95% CIs"),
                                           ggplot(creatorRegisteredMonthCnt_contrast, 
                                                  aes(y = estimate, x = contrast, ymin = lower.CL, ymax = upper.CL)) +
                                             geom_point() + geom_linerange() + geom_hline(yintercept = 0, lty = 2) +
                                             labs(x = "Cluster", y = "Average Creator Registered Month Count", colour = "Cluster", 
                                             title = "Difference Between the Average Creator Registered Month Counts for Each Cluster", 
                                             subtitle = "Error bars are 95% CIs"))

followCnt_lm <- lm(value ~ cluster, cluster_summary_followCnt)
followCnt_emm <- emmeans(followCnt_lm, ~ cluster)
followCnt_contrast <- confint(pairs(followCnt_emm, reverse = TRUE))
avg_followCnt <- grid.arrange(ggplot(summary(followCnt_emm), aes(y = emmean, x = cluster, ymin = lower.CL, ymax = upper.CL, color = cluster)) +
                          geom_point() + geom_linerange() + geom_hline(yintercept = 0, lty = 2) +
                                             labs(x = "Cluster", y = "Average User Follow Count", colour = "Cluster", 
                                             title = "Average User Follow Count for Each Cluster", 
                                             subtitle = "Error bars are 95% CIs"),
                        ggplot(followCnt_contrast, aes(y = estimate, x = contrast, ymin = lower.CL, ymax = upper.CL)) +
                          geom_point() + geom_linerange() + geom_hline(yintercept = 0, lty = 2) +
                                             labs(x = "Cluster", y = "Average User Follow Count", colour = "Cluster", 
                                             title = "Difference Between the Average User Follow Counts for Each Cluster", 
                                             subtitle = "Error bars are 95% CIs"))
```

## Perspective 2
```{r}
data_for_demo <- modelling_data_for_clusters %>% dplyr::select(c("province", "age", "type", "publishTime", "userRegisteredMonthCnt",
                                                          "creatorRegisteredMonthCnt", "followCnt", "userGender", "isActive"))

data_for_demo <- data_for_demo %>% filter(isActive == 1)
data_for_demo$isActive <- NULL
data_for_demo <- data_for_demo %>% mutate(type = ifelse(type == 1, "Image", "Video"))
data_for_demo <- data_for_demo %>% mutate(userGender = ifelse(userGender == 1, "femaleUser", "maleUser"))

data_for_demo <- data_for_demo %>%
  group_by(province, userGender, type) %>%
  dplyr::summarise(age = mean(age),
            publishTime = mean(publishTime),
            userRegisteredMonthCnt = mean(userRegisteredMonthCnt),
            creatorRegisteredMonthCnt = mean(creatorRegisteredMonthCnt),
            followCnt = mean(followCnt)) %>%
  tidyr::pivot_wider(names_from = c(userGender, type), values_from = c(age, publishTime, userRegisteredMonthCnt, creatorRegisteredMonthCnt,
                                                                       followCnt), 
                     values_fill = 0)

data_for_demo <- data_for_demo %>% remove_rownames %>% column_to_rownames(var="province")
data_for_demo_scaled <- scale(data_for_demo)

# Scree plot for remaining attributes
wss <- 0

set.seed(123)
for(i in 1:20){
  km.out <- kmeans(data_for_demo_scaled, centers = i, nstart = 25)
  wss[i] <- km.out$withinss

  print(i)
}

plot(wss, type = "b", xlab = "Number of Clusters", ylab = "Within groups sum of squares", main = "Scree Plot for Clustering Provinces")

set.seed(123)
kmeans_demo <- kmeans(data_for_demo, centers = 4, nstart = 25)
data_for_demo$cluster <- kmeans_demo$cluster

fviz_cluster(kmeans_demo, data = data_for_demo)
table(data_for_demo$cluster)
summary_demo <- aggregate(data_for_demo, by = list(cluster = kmeans_demo$cluster), mean)
summary_demo <- round(summary_demo, 0)
```   

# R Package Citations
```{r}
citation("RSQLite")
citation("dplyr")
citation("tidyverse")
citation("data.table")
citation("emmeans")
citation("stringR")
citation("gridExtra")
citation("MASS")
citation("mice")
citation("mltools")
citation("FactoMineR")
citation("plyr")
citation("ROSE")
citation("corrplot")
citation("ppclust")
citation("cluster")
citation("flashClust")
citation("factoextra")
citation("FSelector")
citation("caTools")
citation("e1071")
citation("caret")
citation("caretEnsemble")
citation("Amelia")
citation("Hmisc")
citation("stargazer")
citation("utils")
```
